### 2024-11-26 article.qmd
Update Acknowledgements

N. Fernandez-Anez acknowledges The Research Council of Norway, Project 301569: Building Design for At-risk Groups (BUILDER) for supporting her contribution. F. Vermina Plathner was supported by FORMAS \[grant number 2021-02396\]. E. Pastor acknowledges the Spanish Ministry of Science, Innovation and Universities, Project PID2023-150607OB-I00.

>>>>

This work was partially supported by an Short-Term Scientific Mission Grant from the COST Action CA18134 FIRElinks.N. Fernandez-Anez acknowledges The Research Council of Norway, Project 301569: Building Design for At-risk Groups (BUILDER) for supporting her contribution. F. Vermina Plathner was supported by FORMAS \[grant number 2021-02396\]. E. Pastor acknowledges the Spanish Ministry of Science, Innovation and Universities, Project PID2023-150607OB-I00. Building data have been downloaded from Geofabrik GmbH (<https://www.geofabrik.de/>). Map data copyrighted OpenStreetMap contributors and available from [https://www.openstreetmap.org](https://www.openstreetmap.org/). This publication has been prepared using European Union's Copernicus Land Monitoring Service information: <https://doi.org/10.2909/960998c1-1870-4e82-8051-6485205ebbac>.
